---
title: "Accurate Scientific Impact and Citations Tracker"
format: html
execute: 
    echo: false
    cache: false
    warning: false
---

This application tracks the scientific impact of leading scholars in political science. Data is retrieved from Google Scholar and updated `r lubridate::today()`.

```{r}
#| label: calcimpact

pacman::p_load(tidyverse, scholar, kableExtra)

get_impact_stats <- function(gs_id, author_name_pattern) {
  profile <- get_profile(gs_id)

  pubs <- get_publications(gs_id) |>
    mutate(
      pub_no = row_number(),
      n_authors = str_count(author, ",") + 1,
      .before = 1
    ) |>
    separate_longer_delim(cols = author, delim = ",") |>
    group_by(pub_no) |>
    mutate(author_no = row_number()) |>
    ungroup() |>
    filter(str_detect(author, author_name_pattern))

  lst(
    n_articles = get_num_articles(gs_id),
    total_cites = profile$total_cites,
    h_index = profile$h_index,
    i10_index = profile$i10_index,
    effective_cites = pubs |>
      group_by(pub_no) |>
      mutate(effective = cites / n_authors) |>
      ungroup() |>
      summarise(effective_sum = sum(effective)) |>
      pull(effective_sum),
    first_author = pubs |>
      summarise(first_share = 100 * sum(author_no == 1) / n()) |>
      mutate(first_share = replace_na(first_share, 0)) |>
      pull(first_share),
    single_author = pubs |>
      summarise(single_share = 100 * sum(n_authors == 1) / n()) |>
      mutate(single_share = replace_na(single_share, 0)) |>
      pull(single_share)
  )
}

sds_stats <- get_impact_stats("TeuKGQ0AAAAJ", "Damsbo")
fkk_stats <- get_impact_stats("2jFLHrgAAAAJ", "Larsen|Kjøller")
chd_stats <- get_impact_stats("cgRByH8AAAAJ", "Dausgaard")

```

```{r}
#| label: showimpact

ready_stats <- bind_rows(
    bind_rows(sds_stats) |> 
    mutate(person = "Søren Damsbo-Svendsen", .before = 1),
    bind_rows(fkk_stats) |> 
    mutate(person = "Frederik K. Kjøller", .before = 1),
    bind_rows(chd_stats) |> 
    mutate(person = "Christoffer H. Dausgaard", .before = 1)) |> 
    pivot_longer(cols = where(is.numeric), names_to = "stat", values_to = "val") |> 
    pivot_wider(names_from = "person", values_from = "val") |> 
    mutate(stat_lab = case_match(stat, 
            "n_articles" ~ "No. Articles",
            "total_cites" ~ "Total Citations",
            "h_index" ~ "h-index",
            "i10_index" ~"i10-index",
            "effective_cites" ~ "Effective Citations Index™️",
            "first_author" ~ "Pivotal Contributor Index™️",
            "single_author"~"Pioneer Index™️"), .after = stat)

write_csv(ready_stats, here::here("Data", paste0("impact-tracker_", lubridate::today(), ".csv")))

stats_ratio <- ready_stats |> 
  rowwise() |> 
   transmute(stat_lab, ratio = `Søren Damsbo-Svendsen` / max(c(`Frederik K. Kjøller`, `Christoffer H. Dausgaard`))) |> 
   ungroup()

  stats_ratio_max <- stats_ratio |> 
    filter(ratio == max(ratio))

ready_stats |>
  mutate(stat = factor(stat, levels = c("total_cites", "n_articles", "h_index", "i10_index", "effective_cites", "first_author", "single_author"))) |>
  arrange(stat) |>
  select(-stat) |>
    rename('Impact Metric' = stat_lab) |>
    kable(
      format = "html",
      digits = 0,
      col.names = c(
        'Impact Metric',
        '<a href="https://scholar.google.com/citations?user=TeuKGQ0AAAAJ&hl=en&oi=sra" target="_blank" title="Link to Google Scholar profile">Søren Damsbo-Svendsen</a>',
        '<a href="https://scholar.google.com/citations?user=2jFLHrgAAAAJ&hl=da" target="_blank" title="Link to Google Scholar profile">Frederik K. Kjøller</a>',
        '<a href="https://scholar.google.com/citations?user=cgRByH8AAAAJ&hl=da" target="_blank" title="Link to Google Scholar profile">Christoffer H. Dausgaard</a>'
      ),
      escape = FALSE
    )

```

Note that we recommend relying primarily on `r stats_ratio_max$stat_lab`, which provides the most accurate picture of a researcher's impact, integrity, and overall character and is highly superior to existing metrics.

## Methodology

Out-dated impact metrics such as *Total Citations* can be wildly misleading (Damsbo-Svendsen `r lubridate::year(lubridate::today())`), which has led to the invention of novel, much more accurate measures:

- The **Effective Citations Index™️** (Damsbo-Svendsen `r lubridate::year(lubridate::today())`) deflates artificially high raw citations numbers for co-authored publications by the number of co-authors, yielding the effective *personal* number of citations:
$$\text{ECI} = \sum_{i=1}^{N} \frac{c_i}{a_i}$$
  where $c_i$ is the citation count and $a_i$ the number of authors for publication $i$.

- The **Pivotal Contributor Index™️** (Damsbo-Svendsen `r lubridate::year(lubridate::today())`) highlights significant and pivotal contributions to science. It is calculated as the share of publications where an author is lead-author:
$$\text{PCI} = \frac{1}{N}\sum_{i=1}^{N} \mathbf{1}[\text{rank}_i = 1] \times 100$$
  where $\text{rank}_i = 1$ indicates that the author appears first on publication $i$.

- The **Pioneer Index™️** (Damsbo-Svendsen `r lubridate::year(lubridate::today())`) is a method for identifying field-leading scholarly efforts. It is calculated as the share of publications which an author has created independently and *cutting-edgedly* based on their own brilliant ideas, without disturbance from co-authors:
$$\text{PI} = \frac{1}{N}\sum_{i=1}^{N} \mathbf{1}[a_i = 1] \times 100$$
  where $\mathbf{1}[a_i = 1]$ indicates that publication $i$ has a single author.

## References

Damsbo-Svendsen, S. (`r lubridate::year(lubridate::today())`). Accurate Scientific Impact and Citations Tracker. Personal website of Søren Damsbo-Svendsen. https://soerendamsbo.github.io/impact-tracker.html
