---
title: "Accurate Scientific Impact and Citations Tracker"
format: html
execute: 
    echo: false
    cache: false
---

This application tracks the scientific impact of leading scholars in political science. Data is retrieved from Google Scholar and updated `r lubridate::today()`.

```{r}

pacman::p_load(tidyverse, scholar, kableExtra)

################################################################
## Søren ----
################################################################

id <- "TeuKGQ0AAAAJ" # scholar ID
sds_stats <- lst()    # empty results list

# Count articles
sds_stats$n_articles <- get_num_articles(id)

# Retrieve cite report
sds_tmp_stats <- get_profile(id)

# Save cite report
sds_stats$total_cites <- sds_tmp_stats$total_cites
sds_stats$h_index <- sds_tmp_stats$h_index
sds_stats$i10_index <- sds_tmp_stats$i10_index

# Retrieve publications and calculate author order and number
sds_pubs <- get_publications(id) |>
  mutate(
    pub_no = row_number(),
    n_authors = str_count(author, ",") + 1,
    .before = 1
  ) |>
  separate_longer_delim(cols = author, delim = ",") |>
  group_by(pub_no) |>
  mutate(author_no = row_number()) |>
  ungroup() |>
  filter(str_detect(author, "Damsbo"))

# Calculate Effective CitationsTM
sds_stats$effective_cites <- sds_pubs |>
  group_by(pub_no) |>
  mutate(effective = cites / n_authors) |>
  ungroup() |>
  summarise(effective_sum = sum(effective)) |>
  pull(effective_sum)

# Calculate Very Important First-Author Share IndexTM
sds_stats$first_author <- sds_pubs |>
    summarise(first_share = 100 * sum(author_no == 1) / n()) |>
  mutate(first_share = replace_na(first_share, 0)) |> 
  pull(first_share)

sds_stats$single_author <- sds_pubs |>
    summarise(single_share = 100 * sum(n_authors == 1) / n()) |>
  mutate(single_share = replace_na(single_share, 0)) |> 
  pull(single_share)

################################################################
## Frederik ----
################################################################

id <- "2jFLHrgAAAAJ" # scholar ID
fkk_stats <- lst()    # empty results list

# Count articles
fkk_stats$n_articles <- get_num_articles(id)

# Retrieve cite report
fkk_tmp_stats <- get_profile(id)

# Save cite report
fkk_stats$total_cites <- fkk_tmp_stats$total_cites
fkk_stats$h_index <- fkk_tmp_stats$h_index
fkk_stats$i10_index <- fkk_tmp_stats$i10_index

# Retrieve publications and calculate author order and number
fkk_pubs <- get_publications(id) |>
  mutate(
    pub_no = row_number(),
    n_authors = str_count(author, ",") + 1,
    .before = 1
  ) |>
  separate_longer_delim(cols = author, delim = ",") |>
  group_by(pub_no) |>
  mutate(author_no = row_number()) |>
  ungroup() |>
  filter(str_detect(author, "Larsen|Kjøller"))

# Calculate Effective CitationsTM
fkk_stats$effective_cites <- fkk_pubs |>
  group_by(pub_no) |>
  mutate(effective = cites / n_authors) |>
  ungroup() |> 
  summarise(effective_sum = sum(effective)) |>
  pull(effective_sum)

# Calculate Very Important First-Author Share IndexTM
fkk_stats$first_author <- fkk_pubs |>
  summarise(first_share = 100 * sum(author_no == 1) / n()) |>
  mutate(first_share = replace_na(first_share, 0)) |> 
  pull(first_share)

# Calculate Very Important Single-Author Share IndexTM
fkk_stats$single_author <- fkk_pubs |>
    summarise(single_share = 100 * sum(n_authors == 1) / n()) |>
  mutate(single_share = replace_na(single_share, 0)) |> 
  pull(single_share)

################################################################
## Christoffer ----
################################################################

id <- "cgRByH8AAAAJ" # scholar ID
chd_stats <- lst()    # empty results list

# Count articles
chd_stats$n_articles <- get_num_articles(id)

# Retrieve cite report
chd_tmp_stats <- get_profile(id)

# Save cite report
chd_stats$total_cites <- chd_tmp_stats$total_cites
chd_stats$h_index <- chd_tmp_stats$h_index
chd_stats$i10_index <- chd_tmp_stats$i10_index

# Retrieve publications and calculate author order and number
chd_pubs <- get_publications(id) |>
  mutate(
    pub_no = row_number(),
    n_authors = str_count(author, ",") + 1,
    .before = 1
  ) |>
  separate_longer_delim(cols = author, delim = ",") |>
  group_by(pub_no) |>
  mutate(author_no = row_number()) |>
  ungroup() |>
  filter(str_detect(author, "Dausgaard"))

# Calculate Effective CitationsTM
chd_stats$effective_cites <- chd_pubs |>
  group_by(pub_no) |>
  mutate(effective = cites / n_authors) |>
  ungroup() |> 
  summarise(effective_sum = sum(effective)) |>
  pull(effective_sum)

# Calculate Very Important First-Author Share IndexTM
chd_stats$first_author <- chd_pubs |>
  summarise(first_share = 100 * sum(author_no == 1) / n()) |>
  mutate(first_share = replace_na(first_share, 0)) |> 
  pull(first_share)

# Calculate Very Important Single-Author Share IndexTM
chd_stats$single_author <- chd_pubs |>
    summarise(single_share = 100 * sum(n_authors == 1) / n()) |>
  mutate(single_share = replace_na(single_share, 0)) |> 
  pull(single_share)

```

```{r}
ready_stats <- bind_rows(
    bind_rows(sds_stats) |> 
    mutate(person = "Søren Damsbo-Svendsen", .before = 1),
    bind_rows(fkk_stats) |> 
    mutate(person = "Frederik K. Kjøller", .before = 1),
    bind_rows(chd_stats) |> 
    mutate(person = "Christoffer H. Dausgaard", .before = 1)) |> 
    pivot_longer(cols = where(is.numeric), names_to = "stat", values_to = "val") |> 
    pivot_wider(names_from = "person", values_from = "val") |> 
    mutate(stat_lab = case_match(stat, 
            "n_articles" ~ "No. Articles",
            "total_cites" ~ "Total Citations",
            "h_index" ~ "h-index",
            "i10_index" ~"i10-index",
            "effective_cites" ~ "Effective Citations Index™️",
            "first_author" ~ "Pivotal Contributor Index™️",
            "single_author"~"Pioneer Index™️"), .after = stat)

write_csv(ready_stats, here::here("Data", paste0("impact-tracker_", lubridate::today(), ".csv")))

stats_ratio <- ready_stats |> 
  rowwise() |> 
   transmute(stat_lab, ratio = `Søren Damsbo-Svendsen` / max(c(`Frederik K. Kjøller`, `Christoffer H. Dausgaard`))) |> 
   ungroup()

  stats_ratio_max <- stats_ratio |> 
    filter(ratio == max(ratio))

ready_stats |> 
  select(-stat) |> 
    rename('Impact Metric' = stat_lab) |> 
    kable(format = "html", digits = 0) 

```

Note that we *strongly* recommend relying primarily on `r stats_ratio_max$stat_lab`, which provides the most accurate picture of a researcher's impact, integrity, and overall character and is highly superior to existing metrics. 

## Methodology

Out-dated impact metrics such as Total Citations can be wildly misleading (Damsbo-Svendsen `r lubridate::year(lubridate::today())`), which has led to the invention of novel, much more accurate measures:

- The **Effective Citations Index™️** (Damsbo-Svendsen `r lubridate::year(lubridate::today())`) deflates artificially high raw citations numbers for co-authored publications by the number of co-authors, yielding the effective *personal* number of citations.
- The **Pivotal Contributor Index™️** (Damsbo-Svendsen `r lubridate::year(lubridate::today())`) highlights significant and pivotal contributions to science. It is calculated as the share of publication, where an author is lead-author.
- The **Pioneer Index™️** (Damsbo-Svendsen `r lubridate::year(lubridate::today())`) is a method for identifying field-leading scholarly efforts. It is calculated as the share of publications, which an author has created independently and *cutting-edgedly* based on their own brilliant ideas, without disturbance from co-authors.

## Google Scholar profile links

- [Søren Damsbo-Svendsen](https://scholar.google.com/citations?user=TeuKGQ0AAAAJ&hl=en&oi=sra)
- [Frederik Klaaborg Kjøller](https://scholar.google.com/citations?user=2jFLHrgAAAAJ&hl=da)
- [Christoffer Hentzer Dausgaard](https://scholar.google.com/citations?user=cgRByH8AAAAJ&hl=da)

## References

Damsbo-Svendsen, S. (`r lubridate::year(lubridate::today())`). Accurate Scientific Impact and Citations Tracker. Personal website of Søren Damsbo-Svendsen. https://soerendamsbo.github.io/impact-tracker.html^[Beware that references from within this site are not included in the impact estimates.]

